Finding the True MVP

### 2024-12-03 paper/paper.qmd
Edits to paper

# Create a styled table using kable
combined_table %>%
  kable(
    format = "html",
    col.names = c(
      "Year",
      "Simulated Data - Player",
      "Simulated Data - MVP Index",
      "Historical Data - Player",
      "Historical Data - MVP Index"
    )
  ) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
  add_header_above(c(" " = 1, "Simulated Data" = 2, "Historical Data" = 2))

@@

```{r}
# Extract the summary of the model
lm_summary <- summary(lm_model)

# Extract coefficients as a data frame
coef_table <- as.data.frame(lm_summary$coefficients)
colnames(coef_table) <- c("Estimate", "Std. Error", "t value", "Pr(>|t|)")

# Create the kable table
kable(coef_table, caption = "Linear Regression Model Coefficients") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

>>>>

# Create a styled table using kable
combined_table %>%
  kable(
    format = "latex",
    booktabs = TRUE,
    col.names = c(
      "Year",
      "Simulated Data - Player",
      "Simulated Data - MVP Index",
      "Historical Data - Player",
      "Historical Data - MVP Index"
    )
  ) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
  add_header_above(c(" " = 1, "Simulated Data" = 2, "Historical Data" = 2))

@@

```{r}
lm_summary <- summary(lm_model)
